LAGOS lake depth

### 2020-06-18 figures/01_geometry.Rmd
align geometry grid

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) + 
  geom_point(size = 1) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to lake center (m)")

gg_scatter_reservoir <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  ggplot() + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = reservoir_class), 
             size = 1) +
  scale_color_discrete(labels = c("NL     ", "Res")) + 
  # geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Deepest point distance (m)") +
  ylab("Distance to lake center (m)")
```

@@

gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) + 
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 2550, y = 300, label = "R^2 == 0.80",
                                parse = TRUE, size = text_size) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to lake center (m)") +
  xlim(0, 3000) +
  theme_opts

>>>>

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) + 
  geom_point(size = 1) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)")

gg_scatter_reservoir <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  ggplot() + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = reservoir_class), 
             size = 1) +
  scale_color_discrete(labels = c("NL     ", "Res")) + 
  # geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)")
```

@@

gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) + 
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 2550, y = 300, label = "R^2 == 0.80",
                                parse = TRUE, size = text_size) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  xlim(0, 3000) +
  theme_opts
